---
title: "data-step1"
author: "ShibeiXu & WenyiLiu"
date: "2021/11/19"
output:html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#Loading library and theme setting
library(haven)
library(tidyverse)
library(rvest)
library(viridis)
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,fig.width = 8, fig.height = 6,out.width = "90%")
options(ggplot2.continuous.colour = "viridis",ggplot2.continuous.fill = "viridis")
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Load the dataset and check the dataset

```{r}
abuse=read_sas("abuse.sas7bdat")
summary(abuse)
```
## Data wrangling

```{r}
abuse_1=abuse%>%
select(pyear,agegrp,outcome,area,BSAE)%>%
filter(outcome%in% c("COCYR", "IEMMON","MRJMON","SUMMON","INCIDENCE","BNGALC","RISKMJ"))%>%
mutate(outcome=as.factor(outcome),
       pyear=as.factor(pyear),
       agegrp=as.factor(agegrp),
       area=as.factor(area),
       BSAE=as.numeric(BSAE))%>%
pivot_wider(names_from = outcome,values_from = BSAE)%>%
  unnest(cols = everything() )
```

## The trends in illicit drug use in the past month in different age and area group
```{r}
abuse_1%>%
  group_by(pyear,agegrp,area)%>%
  summarize(
  mean_SUMMON = mean(SUMMON)
)%>%
  ggplot(aes(x = pyear, y = mean_SUMMON)) +
  facet_grid(~area) +
  geom_point(aes(color = agegrp), alpha = .5)
```

## The trends in alcohol use in different age and area group
```{r}
abuse_1%>%
  group_by(pyear,agegrp,area)%>%
  summarize(
  mean_BNGALC = mean(BNGALC)
)%>%
  ggplot(aes(x = pyear, y = mean_BNGALC)) +
  facet_grid(~area) +
  geom_point(aes(color = agegrp), alpha = .5)
```

## The trends in Marijuana use in different age and area group
```{r}
abuse_1%>%
  group_by(pyear,agegrp,area)%>%
  summarize(
  mean_MRJMON = mean(MRJMON)
)%>%
  ggplot(aes(x = pyear, y = mean_MRJMON)) +
  facet_grid(~area) +
  geom_point(aes(color = agegrp), alpha = .5)
```

##Trends of Marijuana used in last month, filter in area
```{r}
abuse_1%>%
  group_by(pyear)%>% 
  filter(area==1)%>% 
  summarize( mean_MRJMON = mean(MRJMON), )%>% ggplot(aes(x = pyear, y = mean_MRJMON,group=1)) + geom_line()+geom_point()
```

##Trends of illicit drug use other than marijuana used in last month, filter in area
```{r}
abuse_1%>%
  group_by(pyear)%>% 
  filter(area==1)%>% 
  summarize( mean_IEMMON= mean(IEMMON), )%>% ggplot(aes(x = pyear, y = mean_IEMMON,group=1)) + geom_line()+geom_point()
```

##Trends of average annual rate of first use of marijuana, filter in area
```{r}
abuse_1%>%
  group_by(pyear)%>%
  filter(area==1)%>%
  summarize(
  mean_INCIDENCE = mean(INCIDENCE),
)%>%
  ggplot(aes(x = pyear, y = mean_INCIDENCE,group=1)) + 
  geom_line()+geom_point()
```

##Trends of perceptions of great risk from smoking marijuana once a month, filter in area
```{r}
 abuse_1%>%
  group_by(pyear)%>%
  filter(area==1)%>%
  summarize(
  mean_RISKMJ = mean(RISKMJ),
)%>%
  ggplot(aes(x = pyear, y = mean_RISKMJ,group=1)) + 
  geom_line()+geom_point()
```

##Trends of alcohol, filter in area
```{r}
 abuse_1%>%
  group_by(pyear)%>%
  filter(area==1)%>%
  summarize(
  mean_BNGALC = mean(BNGALC),
)%>%
  ggplot(aes(x = pyear, y = mean_BNGALC,group=1)) + 
  geom_line()+geom_point()
```
